\documentclass{article}
\usepackage{geometry}
\usepackage[namelimits,sumlimits]{amsmath}
\usepackage{amssymb,amsfonts}
\usepackage{multicol}
\usepackage{mathrsfs}
\usepackage[cm]{fullpage}
\newcommand{\nc}{\newcommand}
\newcommand{\tab}{\hspace*{5em}}
\newcommand{\conj}{\overline}
\newcommand{\dd}{\partial}
\nc{\cn}{\mathbb{C}}
\nc{\rn}{\mathbb{R}}
\nc{\qn}{\mathbb{Q}}
\nc{\zn}{\mathbb{Z}}
\nc{\aff}{\mathbb{A}}
\nc{\proj}{\mathbb{P}}
\nc{\pd}[2]{\frac{\partial {#1}}{\partial {#2}}}
\nc{\ep}{\epsilon}
\nc{\topo}{\mathscr{T}}
\nc{\basis}{\mathscr{B}}
\nc{\nullset}{\varnothing}
\nc{\openm}{\begin{pmatrix}}
\nc{\closem}{\end{pmatrix}}
\DeclareMathOperator{\Gr}{Gr}
\begin{document}
Name: Hall Liu

Date: \today 
\vspace{1.5cm}

I'll probably be referencing Algebraic Geometry -- a First Course (Harris) a lot in this pset -- it's a lot more helpful than our textbook.
\subsection*{5.5.1}
If $V$ is a linear subvariety, then it is defined by $x_i=0$ for some set of $i$s after a linear change of variables. This is the intersection of a bunch of hypersurfaces defined by degree $1$ polynomials, so it has degree $1$.

Conversely, suppose $V$ has degree $1$ and dimension $d>0$. Further, suppose that $V$ is not a linear variety. Then, for some point $p\in V$, $V$ and $T_pV$ intersect with $\dim(V\cap T_pV)\leq 2d-n$ (I don't know how to formally prove this, but it seems to be true intuitively in low dimensions). Choose some subspace or superspace $W$ containing $p$ of $T_pV$ of dimension $n-d$ such that $W$ intersects $V$ at a finite number of points (again, no formal proof, but it seems right). Due to the definition of degree, $W\cap V$ consists of only the point $p$. However, $W$ and $V$ do not intersect transversely, since the dimension of the span of the tangent spaces of $W$ and $V$ is $\max(\dim T_pV, \dim W)$ since we have $T_pW=W$ and either $T_pV\subset W$ or $W\subset T_pV$. Thus, the intersection multiplicity at $p$ must be greater than $1$. However, by Thm 18.4 from Harris, $\deg W\cdot\deg V=1$ is the sum of the intersection multiplicities at all the subvarieties on which they intersect, but we showed that this must be greater than $1$. Thus, $V$ being nonlinear is a contradiction.
\subsection*{5.5.3}
Consider the conics $V(x^2+y^2-z^2)$ and $V(xy)$. Since these are both hypersurfaces formed from degree $2$ polynomials, they both have degree $2$. The example on page 94 shows that $V(x^2+y^2-z^2)$ is smooth, but if we examine the Jacobian of $xy$ at $[0:0:1]$, it's zero, so it has rank zero, which means that the dimension of the tangent space there is $2$, which disagrees with the dimension of the variety. Therefore they're not isomorphic.
\subsection*{5.6.1}
Let $W=v_d(V)$ and $p\in k[W]_n$, a degree $n$ polynomial. There exists a homomorphism from $k[W]_n$ to $k[V]_{nd}$ that's formed by taking the pullback $p\circ v_d$ of the Veronese map, so $p$ composed with the degree $d$ monomials from the Veronese map gives a degree $nd$ polynomial in $k[V]$. This map is injective, since if $p\circ v_d$ vanishes on $V$, then $p$ must vanish on the image of $V$, or $k[W]$, so $p$ is zero. This map is surjective, since we can express any degree $nd$ monomial as an appropriate product of the Veronese coefficients (i.e. $x_i^ax_j^b$ where $a+b=d$, proof later). Thus, the dimensions of $k[W]_n$ and $k[V]_{nd}$ are equal, so the Hilbert polynomial of $W$ is $P(nd)$, where $P$ is the Hilbert polynomial of $V$.

Proof of the monomial thingy: Let the monomial be $x_1^{j_1}\cdots x_k^{j_k}$, sum of the $j_i$ is $nd$. First, factor out all the $x_i^d$s, leaving behind only powers of $x_i$ less than $d$ and which powers sum up to a multiple of $d$. Then, match up all the powers of $x_1$ with a corresponding number of powers of $x_2$ (so that they add up to $d$) and remove them as a factor, do the same thing with the remaining powers of $x_2$ with $x_3$, and so on. This is guaranteed to leave nothing behind since we started with a multiple of $d$ total powers and are removing $d$ every time.
%Consider some $g\in k[V]$ of degree $n$. The inverse of the Veronese map induces a homomorphism from $k[V]$ to $k[W]$, so the image of $g$ is $g\circ F$, where $F$ is the inverse of the Veronese map. This is an element of $k[W]_n$, since $F$ is a projection. However, we can also view $g\circ F$ as an element of $k[V]_{nd}$ by ``loading in'' the degree $d$ monomials (in the coordinates of $V$) that are the coordinates of $W$. 
\subsection*{3}
Consider linear forms on the space $\proj(\bigwedge^k V)$, the space in which the Grassmannian $\Gr(k,n)$ is embedded. The complements of the zeros of these forms, intersected with the Grassmannian, form an open cover of the Grassmannian, since there is no point on the Grassmannian where all linear forms vanish. Call these intersections the $V_i$. Following the argument from Harris, p65, we have that these $V_i$ are isomorphic to $\aff^{k(n-k)}$, which means that they're irreducible. Now, take a finite subcover $V_1,\ldots,V_r$, and suppose $\Gr(k,n)=G_1\cup G_2$. Then, for each $i$, we have $V_i=(V_i\cap G_1)\cup(V_1\cap G_2)$. Since $V_1$ is irreducible, we can assume WLOG that $V_1\subset G_1$, so $V_i\cap V_1\subset G_1$ for all $i$. Now, $V_1\cap V_i$ is nonempty, since the dimension of each $V_i^c$ is $1$ and the Grassmannian has higher dimension (the ones not equal to $\proj^n$ anyway), so $V_1\cap V_i$ is open therefore dense in $V_i$. Taking the closure, we get $V_i$, so $V_i\subset G_1$ as well because $G_1$ is closed. Thus we have $\Gr(k,n)=G_1$. 
\subsection*{5}
a. The point $x$ is contained in some open affine subset of $\proj^3$, and since lines are determined by their restriction to some open affine subset, we can instead consider the set of lines passing through some point $x\in\aff^3$ instead. By translating $x$ to the origin, we see that this set of lines is in fact $\Gr(1,3)=\proj^2$. To show that it's a subvariety of $\Gr(2,4)$, note that lines in $\proj^3$ are synonymous with dimension $2$ subspaces of $\aff^4$ by taking the affine cone, and the requirement that a line pass through $p$ translates to the plane containing some line through the origin in $\aff^4$. This means that to span the plane, we need to fix one vector $p$ and pick some other $v$ not linearly dependent with $p$, so the image under the Plucker embedding is the set of products $p\wedge v$. Since the image of $\Gr(2,4)$ under the embedding is all products of the form $v_1\wedge v_2$, this is the condition that $v_1=p$, and it's a polynomial condition because if we expand it out in terms of some basis of $\bigwedge^2 \aff^4$, we get a polynomial in each coordinate of the coordinates of $v_1,v_2$.

b. Moving into $\aff^4$ again, the planes in $\proj^3$ correspond to $3$-dimensional subspaces of $\aff^2$ and the lines contained therein correspond to affine planes in those $3$-dimensional subspaces. Since we can associate $2$-d subspaces of $\aff^3$ to $1$-d subspaces by taking the orthogonal complement, this again corresponds to $\proj^2$. Now, using the argument above, instead of the plane in $\aff^4$ having to contain some line, we now need the plane to be orthogonal to some line $l$ determined by the orthogonal complement of the copy of $\aff^3$ that the plane $P\subset\proj^3$ corresponds to. If we let $l$ be the set of multiples of some vector $v$, this is the requirement (using the notation from above) that $v_1\cdot v=0$ and $v_2\cdot v=0$, which is once again a polynomial condition.
\subsection*{6}
a. If $\dim X=0$, then either $|X|=0$ or $1$, or $X$ is reducible but its only irreducible components are points. Thus, we want to show that projective varieties must only contain a finite number of irreducible components. For the sake of contradiction, suppose $X$ can only be written as the union of infinitely many irreducible components. Consider the set of subvarieties of $X$ that also have this property partially ordered under inclusion. It has a minimal element $Y$ due to Zorn's lemma because every descending chain terminates due to the Noetherian condition on homogeneous ideals. $Y$ is reducible, so we can write it as $Y_1\cup Y_2$, but both $Y_1$ and $Y_2$ can be written as the finite union of irreducible components due to minimality of $Y$. Thus such a minimal element does not exist, and $X$ must be finite.

If $X$ is finite, then any of its subvarieties besides the single point is reducible, so the chain of irreducible subvarieties has length $0$.

%b. Induct on $d$. For $d=0$, we have that $X$ is finite. Since there are an infinite number of disjoint $n-1$-dimensional linear subspaces of $\proj^n$, some of them must not intersect $X$, and any $n$-dimensional subspace of $\proj^n$ is the whole thing, which includes $X$. Now, let $\dim X=d$ and suppose it's true for all $k<d$. Then, for some hypersurface $V(f)$ not containing an irreducible component of $X$, there exists some $(n-d)$-dimensional plane $P$ that does not intersect $Y=X\cap V(f)$. Since we had a lot of freedom in choosing the hypersurface and the plane, it's probably safe to say that we can choose $f$ and the plane carefully enough that we get $|P\cap X|=\deg X$ (it's a bit difficult to make this formal). Since $\deg X$ is finite, we can use the argument from earlier to show that there's some $(n-d-1)$-dimensional plane that doesn't intersect $X$.
b. Suppose $\dim X=d$, and take some $(n-d)$-dimensional plane $P$ such that $\deg X=|X\cap P|$. We can do some coordinate changes so that these finite number of points all lie in the same affine patch. We have an infinite number of $(n-d-1)$-dimensional planes in $P$ that do not intersect within this patch, which implies that there exists some $(n-d-1)$-dimensional plane that doesn't hit $X$ at all. Conversely, ... something something
\subsection*{7}
The $k$-dim linear subspace is generated by the ideal $I=(f_1,\ldots,f_{n-k})$ where the $f_i$ are linearly independent homogeneous linear equations. We want to find the dimension of the $i$th grading of this ideal. Do a change of coordinates so that $f_i=x_i$. Then, the $i$th grading of the ideal has a basis consisting of the degree $i$ monomials in $n-k$ variables, of which there are $\binom{n-k+i-1}{i}$. Thus, the Hilbert function is the dimension of the $i$th grading of the whole ring minus this, or $\binom{n+i-1}{i}-\binom{n-k+i-1}{i}$.
\subsection*{8}
Examine the space $I_m$ of degree $m$ homogeneous polynomials. Consider a map $\psi:I_m\to k^d$, $f\mapsto (f(p_1),\ldots,f(p_d))$. We wish to show that this map is surjective, for then we would have that $\ker(\psi)$ is the space of polynomials which vanish on the $d$ points $p_1,\ldots,p_d$, and it'll have degree $\binom{m+n-1}{m}-d$, so subtracting this from $\binom{m+n-1}{m}$ would give $d$.

To show that the map is surjective, we need to show that for each $i$ we can find some $f$ such that $f(p_i)=1$ and $f(p_j)=0$ for $j\neq i$. A point in $\proj^n$ corresponds to a line through the origin in $\aff^{n+1}$, which is defined by the homogeneous linear equation $\sum a_ix_i$. Thus, to make the $f(p_j)$ be zero, we can take a polynomial that's the product of the polynomials corresponding to the $p_j$. This will have degree $n-1\leq m$. Then, we can just pad it up with extra linear factors which don't vanish at $p_i$ to get the desired $f$.
\end{document}
